Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012

### 2018-07-19 paper/ijm.tex
Reacted to one more comment about descriptive table
Added couple of references which might be useful for the CEE comparison stuff

\citet{leslie+lindley2001} analyse both employment and income but
focus on a single year and English language only.
\citet{YaoandOurs2015} only analyse the role of Dutch language
on labour market performance in Netherlands.  
\fxwarning{ot:add CEE stuff here?}
\fxwarning{SKB: Let's collect first enough material and then decide, but I can start adding here some notes from \cite{Kahanec2009,Kahanec2010}.}
%Start here CEE stuff for now
\cite{Kahanec2009} provide an overview about \enquote{the roles of foreign origin and citizenship in the labor markets of Eastern and Eestern[sic] Member States of the EU} \dots and use the EU Survey of Income and Living Conditions (EU-SILC) dataset.
They\enquote{ mapped and compared the roles of foreign origin and citizenship for labor market performance in Eastern and Western EU Member States.}
Using Oaxaca and Fairlie decompositions, they show that there is native/non-native divide in the national labour markets \dots.
They find that \enquote{both foreign origin and citizenship remain important barriers to non-native labor market integration}
\enquote{In Estonia and Latvia, in particular, employment
	policies seem to be most relevant for non-immigrant non-citizens. Once employed,
	non-nativity may play a less negative role in the labor market for some groups,
	although labor market segmentation remains a significant issue.}
\fxnote{\cite{Kahanec2009} essentially confirms your results in \cite{Leping2008,Toomet2011}}
\cite{Kahanec2010} show that \enquote{the labor market situation of ethnic minorities in the European
	Union. Facing a serious measurement challenge and lacking adequate data, we apply
	several measures of ethnicity and examine various data sources as well as secondary
	evidence. We find significant gaps between ethnic minority and majority populations in
	terms of labor market outcomes.}
%Continue with existing stuff
In case of Estonia,
\citet{Toomet2011} shows that the majority language gives little wage
premium for minority men.  However, he analyses neither women, nor
unemployment.  \citet{Lindemann2013} shows that Estonian fluency
is associated with faster job finding rate while while it does not
explain the lower occupational prestige of Russian speakers.  However,
she only includes recent school graduates in her study.

@@

The average wages, language skills and other explanatory variables together with the relative frequencies for the period 2000--2012 are presented in \cref{tab:descriptive}. We report the data separately for ethnic nationalities (Estonians and Russians) and language
skills (Estonian, Russian and English).
\fxwarning{OT: can you add variable 'year' in this table?  I know it feels a little weird but is great to show time trends.}

>>>>

\citet{leslie+lindley2001} analyse both employment and income but
focus on a single year and English language only.
\citet{YaoandOurs2015} only analyse the role of Dutch language
on labour market performance in Netherlands.  
\fxwarning{ot:add CEE stuff here?}
\fxwarning{SKB: Let's collect first enough material and then decide, but I can start adding here some notes from \cite{Kahanec2009,Kahanec2010}.}
%Start here CEE stuff for now
Comparing the results for Estonia with other Central Eastern European (CEE) countries and former Soviet Union countries is rather difficult due to the lack of data about language skills.
Information about ethnicity is widely available, but no information about individual native and foreign language skills.
For example, the Latvian Labour Force Survey does not (did not) contain questions regarding language skills.
While the language policies in the Baltic states are discussed in \cite{Hogan-Brun2008,Hogan-Brun2007}, the implications for the labour market are not discussed.
\cite{Grasmane2011} use information from a survey conducted at the Latvian University of Agriculture with undergraduate, master, doctoral students to find out  how foreign language skills impact employability.
They find that the better foreign language skills are related to higher willingness to work abroad.
\cite{Alan2015} \fxnote{SKB: Quite detailed article about Russian language proficiency in three former Soviet Union states. Needs further comments from us and find similar articles.}
\cite{Kahanec2009} provide an overview about \enquote{the roles of foreign origin and citizenship in the labor markets of Eastern and Eestern[sic] Member States of the EU} \dots and use the EU Survey of Income and Living Conditions (EU-SILC) dataset.
They\enquote{ mapped and compared the roles of foreign origin and citizenship for labor market performance in Eastern and Western EU Member States.}
Using Oaxaca and Fairlie decompositions, they show that there is native/non-native divide in the national labour markets \dots.
They find that \enquote{both foreign origin and citizenship remain important barriers to non-native labor market integration}
\enquote{In Estonia and Latvia, in particular, employment
	policies seem to be most relevant for non-immigrant non-citizens. Once employed,
	non-nativity may play a less negative role in the labor market for some groups,
	although labor market segmentation remains a significant issue.}
\fxnote{\cite{Kahanec2009} essentially confirms your results in \cite{Leping2008,Toomet2011}}
\cite{Kahanec2010} show that \enquote{the labor market situation of ethnic minorities in the European
	Union. Facing a serious measurement challenge and lacking adequate data, we apply
	several measures of ethnicity and examine various data sources as well as secondary
	evidence. We find significant gaps between ethnic minority and majority populations in
	terms of labor market outcomes.}
%Continue with existing stuff
In case of Estonia,
\citet{Toomet2011} shows that the majority language gives little wage
premium for minority men.  However, he analyses neither women, nor
unemployment.  \citet{Lindemann2013} shows that Estonian fluency
is associated with faster job finding rate while while it does not
explain the lower occupational prestige of Russian speakers.  However,
she only includes recent school graduates in her study.

@@

The average wages, language skills and other explanatory variables together with the relative frequencies for the period 2000--2012 are presented in \cref{tab:descriptive}. We report the data separately for ethnic nationalities (Estonians and Russians) and language
skills (Estonian, Russian and English).
\fxwarning{OT: can you add variable 'year' in this table?  I know it feels a little weird but is great to show time trends.}
\fxwarning{SKB: What do you mean with time trends? Which value should a ``year'' variable take? Give me an example, since I don't understand what you want. }
